An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
comment out
pseudo-code for geom_tile

\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}

@@

>>>>

@@

```{r eval=FALSE}
dframe %>% 
  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
    geom_tile() +
    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
    geom_text(aes(label=CMPS.score))
```
